Robotic Manipulator Path Planning Utilizing Interpolated 3D Voxel-Based Obstacle Avoidance Method

### 2023-11-09 Articles/Article 1/main.tex
article structure

%opening
\title{Robotic Arm Path Planning Utilizing Interpolated 3D Voxel-Based Artificial Potential Fields}
\author{}

@@

\section{}

>>>>

 \usepackage{easyReview}

%opening
\title{Robotic Manipulator Path Planning Utilizing Interpolated 3D Voxel-Based Obstacle Avoidance Method}
\author{Jakob Baumgartner, Gregor Klančar}

@@

\section{Introduction}

\section{Related Works}

\add{
	- method was inspired by Khatib APF (however, it evolved into a different method) \\
	- different existing APF manipulator implementation articles \\
	- VFH \\
}

\section{Method}

\add{
	- optimization algorithm \\
	- robot kinematics (include the exact-reduced method) \\
	- primary task of distance goal \\
	- secondary task of repulsive field \\
	- task slowdown option \\
	- secondary task of manipulation measure \\
	- attractive field calculation (normalization of attractive force) \\
	- repulsive field calculation - matrix "convolution" method \\
	- matrix size and shape selection \\
	- PLOT: (ERK) kernel graphics \\
	- PLOT: (ERK) linear kernel graphics \\
	- PLOT: kernel field shape 	\\
	- interpolation of the repulsive field \\
}

\section{Implementation}

\section{Experiments and simulations}

\add{
	- include execution times}
